Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-11 lineages_18Q3.Rmd
delmis/nonsilent tissue Wilcoxon results

knitr::kable(filter(crispr_signif_delmis, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(crispr_signif_delmis_tissue, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

>>>>

knitr::kable(filter(crispr_signif_delmis, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(crispr_signif_delmis_tissue, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```
